Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-10-02 main.tex
Added cryptography proof summary tikz diagram - changed text a tiny bit to reference it nicely Moved tikz image files to their own folder - nicer to keep the imported pdfs and the itkz picture (which aren't imported) seperate

\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize,scale=0.75]
    % Step 1
    \node at (5,22.5) {\small 1. Broadcast and linear combinations step};
    % Navigator
    \node at (1.25,19.25) {Navigator};
    \fill (1.25,18.25) [blue!40] ellipse (0.5 and 0.5);
    % Sensors
    \node at (7.5,21.75) {Sensor $1$};
    \fill [red!40] (5.875,19.75) rectangle (9.5,21.25);
    \node at (7.75,20.5) {$\displaystyle y_1^{(t)} = \sum^m_{j=1}x_{1,j}^{(t)}\omega_j^{(t)}$};
    \node at (7.5,14.75) {Sensor $n$};
    \fill [red!40] (5.875,15.25) rectangle (9.5,16.75);
    \node at (7.75,16) {$\displaystyle y_n^{(t)} = \sum^m_{j=1}x_{n,j}^{(t)}\omega_j^{(t)}$};
    \fill [black] (7.5,18.75) circle (0.05);
    \fill [black] (7.5,17.75) circle (0.05);
    \fill [black] (7.5,18.25) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.75,18.5) (5.75,20.25)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.75,18) (5.75,16.25)};
    \node at (3.5,20.25) {$(\omega_1^{(t)},\dots ,\omega_m^{(t)})$};
    \node at (3.5,16.25) {$(\omega_1^{(t)},\dots ,\omega_m^{(t)})$};

    % Step 2
    \node at (5,13.25) {\small 2. Aggregation step};
    % Navigator
    \node at (3.25,10.75) {Navigator};
    \fill [blue!40] (0.5,8.75) rectangle (5.625,10.25);
    \node at (3,9.5) {$\displaystyle \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}^{(t)}\omega_j^{(t)} = \sum^n_{i=1}y^{(t)}_{i}$};
    % Sensors
    \node at (8.75,12.5) {Sensor $1$};
    \fill  (8.75,7.5) [red!40] ellipse (0.5 and 0.5);
    \node at (8.75,6.5) {Sensor $n$};
    \fill  (8.75,11.5) [red!40] ellipse (0.5 and 0.5);
    \fill [black] (8.75,10) circle (0.05);
    \fill [black] (8.75,9) circle (0.05);
    \fill [black] (8.75,9.5) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(8.25,11.25) (5.75,10)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(8.25,7.75) (5.75,9)};
    \node at (6.75,11.5) {$y_1^{(t)}$};
    \node at (6.75,7.5) {$y_n^{(t)}$};

@@

To show our scheme meets the security notion of LCAO, we prove by contrapositive that for an adversary $\mathcal{A}$ playing against a challenger using \textit{our scheme}, we can create an adversary $\mathcal{A}'$ playing against a challenger using the \textit{Joye-Libert scheme}, such that
\begin{equation*}
    \mathsf{Adv}^{LCAO}(\mathcal{A}) > \eta_1(\kappa) \implies \mathsf{Adv}^{AO}(\mathcal{A}') > \eta_2(\kappa)\,,
\end{equation*}
for some negligible functions $\eta_1$ and $\eta_2$. (\textit{i.e.} if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure.) This is a contradiction to the Joye-Libert AO proof in \cite{joyeScalableSchemePrivacyPreserving2013}, and will thus conclude our proof. The function $H$ used by our scheme is treated as a \textit{random oracle} in the Joye-Libert AO proof and will, therefore, prove our scheme secure in the random oracle model as well.
\begin{pf}
    Consider adversary $\mathcal{A}$ playing the LCAO game defined in Section \ref{subsec:lcao}. The following is a construction of an adversary $\mathcal{A}'$ playing the AO game in Appendix \ref{app:ao} against a challenger $\mathcal{C}$ using the Joye-Libert aggregation scheme from Section \ref{subsec:joye_libert_scheme}.
    \begin{description}
        \item[Setup] When receiving $N$ and $H$ as public parameters from $\mathcal{C}$, choose an $m>1$ and give public parameter $H$, number of weights $m$, and $pk_0=N$ to $\mathcal{A}$.
        \item[Queries] Handle queries from $\mathcal{A}$:
        \begin{description}
            \item[\textit{Weight Query}] When $\mathcal{A}$ submits a weight query $t$, choose weights $\omega^{(t)}_j,\,1 \leq j \leq m$ and random values $r_j \in \mathbb{Z}_N,\,1 \leq j \leq m$, and return encryptions 
            \begin{equation*}
                (N+1)^{\omega^{(t)}_{j}}r_j^N\pmod{N^2},\,1\leq j\leq m
            \end{equation*}
            to $\mathcal{A}$.
            \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,1 \leq j \leq m$ if not already chosen for time $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$. The received response is of the form $(N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $r^N$ for a random $r \in \mathbb{Z}_N$ and return 
            \begin{equation*}
                (N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r^N H(t)^{sk_i} \pmod{N^2}
            \end{equation*}
            to $\mathcal{A}$.
            \item[\textit{Compromise Query}] When $\mathcal{A}$ submits compromise query $i$, make the same compromise query $i$ to $\mathcal{C}$, and return the recieved secret key $sk_i$ to $\mathcal{A}$.
        \end{description}
        \item[Challenge] When $\mathcal{A}$ submits challenge series
        \begin{equation*}
            \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
        \end{equation*}
        and
        \begin{equation*}
            \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
        \end{equation*}
        choose weights $\omega^{(t^*)}_j,1 \leq j \leq m$ for time $t^*$ and submit AO challenge series
        \begin{equation*}
            \langle(i,t^*,\sum^m_{j=1}x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j)\,|\,i \in S\rangle
        \end{equation*}
        and
        \begin{equation*}
            \langle(i,t^*,\sum^m_{j=1}x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j)\,|\,i \in S\rangle\,,
        \end{equation*}
        to $\mathcal{C}$. The received response if of the form 
        \begin{equation*}
            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}H(t^*)^{sk_i}\,|\,i\in U\rangle\,,
        \end{equation*}
        for an unknown $b \in \{0,1\}$. Multiply series elements by $r_i^N,\,1 \leq i \leq n$ for randomly chosen $r_i \in \mathbb{Z}_N$ and return
        \begin{equation*}
            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}r_i^N H(t^*)^{sk_i}\,|\,i\in U\rangle
        \end{equation*}
        to $\mathcal{A}$.
        \item[Guess] When $\mathcal{A}$ makes guess $b'$, make the same guess $b'$ to $\mathcal{C}$.
    \end{description}

@@

\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize,scale=0.9375]
    % Prediction
    \draw  (0,1.75) rectangle (8,8);
    \node at (4,7.5) {\small 1. Prediction};

@@

    % Measurement
    \draw  (0,-4.75) rectangle (8,1.5);
    \node at (4,1) {\small 2. Measurement};

@@

    % Update
    \draw  (0,-10.25) rectangle (8,-5);
    \node at (4,-5.5) {\small 3. Update};

@@

Code was written in the C programming language, using the MPI library \cite{OpenMPI2020} to run simultaneous processes for each sensor and navigator. The OpenSSL library's \cite{OpenSSL2020} mask generation function MGF1 and hash function SHA256 were used to implement the required encryption scheme hash function $H$, while the Libpaillier library \cite{Libpaillier2010} was used for the implementation of the Paillier encryption scheme. Additionally, GNU libraries GSL \cite{GSLGNUScientific2019} and GMP \cite{GMPGNUMultiple2020} were used for algebraic operations and the handling of multiple-precision integers, respectively. Simulation execution was performed on a 3.00GHz Intel i7-9700 CPU, and run on the Windows Subsystem for Linux (WSL), where no real-time kernel was ensured but sufficiently consistent runtimes were observed for the purposes of our simulation.

@@

 \begin{figure}[htbp]
    \begin{center}
       \includegraphics{images/layouts.pdf}
    \end{center}
    \caption{Layouts}
    \label{fig:sim_layouts}
 \end{figure}

>>>>

\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize,scale=0.75]
    % Step 1
    \node at (5,22.5) {1. Broadcast and linear combinations step};
    % Navigator
    \node at (1.25,19.25) {Navigator};
    \fill (1.25,18.25) [blue!40] ellipse (0.5 and 0.5);
    % Sensors
    \node at (7.5,21.75) {Sensor $1$};
    \fill [red!40] (5.875,19.75) rectangle (9.5,21.25);
    \node at (7.75,20.5) {$\displaystyle y_1^{(t)} = \sum^m_{j=1}x_{1,j}^{(t)}\omega_j^{(t)}$};
    \node at (7.5,14.75) {Sensor $n$};
    \fill [red!40] (5.875,15.25) rectangle (9.5,16.75);
    \node at (7.75,16) {$\displaystyle y_n^{(t)} = \sum^m_{j=1}x_{n,j}^{(t)}\omega_j^{(t)}$};
    \fill [black] (7.5,18.75) circle (0.05);
    \fill [black] (7.5,17.75) circle (0.05);
    \fill [black] (7.5,18.25) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.75,18.5) (5.75,20.25)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.75,18) (5.75,16.25)};
    \node at (3.5,20.25) {$(\omega_1^{(t)},\dots ,\omega_m^{(t)})$};
    \node at (3.5,16.25) {$(\omega_1^{(t)},\dots ,\omega_m^{(t)})$};

    % Step 2
    \node at (5,13.25) {2. Aggregation step};
    % Navigator
    \node at (3.25,10.75) {Navigator};
    \fill [blue!40] (0.5,8.75) rectangle (5.625,10.25);
    \node at (3,9.5) {$\displaystyle \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}^{(t)}\omega_j^{(t)} = \sum^n_{i=1}y^{(t)}_{i}$};
    % Sensors
    \node at (8.75,12.5) {Sensor $1$};
    \fill  (8.75,7.5) [red!40] ellipse (0.5 and 0.5);
    \node at (8.75,6.5) {Sensor $n$};
    \fill  (8.75,11.5) [red!40] ellipse (0.5 and 0.5);
    \fill [black] (8.75,10) circle (0.05);
    \fill [black] (8.75,9) circle (0.05);
    \fill [black] (8.75,9.5) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(8.25,11.25) (5.75,10)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(8.25,7.75) (5.75,9)};
    \node at (6.75,11.5) {$y_1^{(t)}$};
    \node at (6.75,7.5) {$y_n^{(t)}$};

@@

To show our scheme meets the security notion of LCAO, we prove by contrapositive that for an adversary $\mathcal{A}$ playing against a challenger using \textit{our scheme}, we can create an adversary $\mathcal{A}'$ playing against a challenger $\mathcal{C}$ using the \textit{Joye-Libert scheme}, such that
\begin{equation*}
    \mathsf{Adv}^{LCAO}(\mathcal{A}) > \eta_1(\kappa) \implies \mathsf{Adv}^{AO}(\mathcal{A}') > \eta_2(\kappa)\,,
\end{equation*}
for some negligible functions $\eta_1$ and $\eta_2$. (\textit{i.e.} if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure.) Given the Joye-Libert AO proof in \cite{joyeScalableSchemePrivacyPreserving2013}, we know our scheme must be LCAO secure and will thus conclude our proof. The proof overview has been given in Figure \ref{fig:proof_summary}. Additionally, the function $H$ used by our scheme is treated as a \textit{random oracle} in the Joye-Libert AO proof and will, therefore, prove our scheme secure in the random oracle model as well.

\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize,scale=0.9375]
    % Bounding box
    \draw [gray] (0,-0.25) rectangle (8,7.5);

    % Outer adversary rectangle
    \draw[rounded corners=15pt, fill=gray!30] (0.5,7) rectangle (7.5,2.75);
    % Inner adversary rectangle
    \draw[rounded corners=15pt, fill=gray!60] (1,6.5) rectangle (7,5.5);

    % Adversaries and challenger
    \node at (4,3.5) {\LARGE$\mathcal{A}'$};
    \node at (4,6) {\LARGE$\mathcal{A}$};
    \node at (4,0.5) {\LARGE$\mathcal{C}$};

    % Arrows
    \node[text width=3cm, align=center] at (2,1.25) {Joye-Libert\\AO scheme};
    \draw [-latex] (2,1.75) -- (2,2.75);

    \node[text width=3cm, align=center] at (2,4) {Our\\LCAO scheme};
    \draw [-latex] (2,4.5) --(2,5.5);

    \node[text width=3cm, align=center] at (6,4) {``Break''\\Our scheme};
    \draw [-latex] (6,5.5) -- (6,4.5);

    \node[text width=3cm, align=center] at (6,1) {``Break''\\Joye-Libert\\scheme};
    \draw [-latex] (6,2.75) -- (6,1.75);
\end{tikzpicture}
\vspace{\baselineskip}
\caption{High-level overview of our scheme's LCAO security proof.}
\label{fig:proof_summary}
\end{figure}

\begin{pf}
    Consider adversary $\mathcal{A}$ playing the LCAO game defined in Section \ref{subsec:lcao}. The following is a construction of an adversary $\mathcal{A}'$ playing the AO game in Appendix \ref{app:ao} against a challenger $\mathcal{C}$ using the Joye-Libert aggregation scheme from Section \ref{subsec:joye_libert_scheme}.
    \begin{description}
        \item[Setup] When receiving $N$ and $H$ as public parameters from $\mathcal{C}$, choose an $m>1$ and give public parameter $H$, number of weights $m$, and $pk_0=N$ to $\mathcal{A}$.
        \item[Queries] Handle queries from $\mathcal{A}$:
        \begin{description}
            \item[\textit{Weight Query}] When $\mathcal{A}$ submits a weight query $t$, choose weights $\omega^{(t)}_j,\,1 \leq j \leq m$ and random values $r_j \in \mathbb{Z}_N,\,1 \leq j \leq m$, and return encryptions 
            \begin{equation*}
                (N+1)^{\omega^{(t)}_{j}}r_j^N\pmod{N^2},\,1\leq j\leq m
            \end{equation*}
            to $\mathcal{A}$.
            \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,1 \leq j \leq m$ if not already chosen for time $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$. The received response is of the form $(N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $r^N$ for a random $r \in \mathbb{Z}_N$ and return 
            \begin{equation*}
                (N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r^N H(t)^{sk_i} \pmod{N^2}
            \end{equation*}
            to $\mathcal{A}$.
            \item[\textit{Compromise Query}] When $\mathcal{A}$ submits compromise query $i$, make the same compromise query $i$ to $\mathcal{C}$, and return the recieved secret key $sk_i$ to $\mathcal{A}$.
        \end{description}
        \item[Challenge] When $\mathcal{A}$ submits challenge series
        \begin{equation*}
            \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
        \end{equation*}
        and
        \begin{equation*}
            \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
        \end{equation*}
        choose weights $\omega^{(t^*)}_j,1 \leq j \leq m$ for time $t^*$ and submit AO challenge series
        \begin{equation*}
            \langle(i,t^*,\sum^m_{j=1}x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j)\,|\,i \in S\rangle
        \end{equation*}
        and
        \begin{equation*}
            \langle(i,t^*,\sum^m_{j=1}x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j)\,|\,i \in S\rangle\,,
        \end{equation*}
        to $\mathcal{C}$. The received response if of the form 
        \begin{equation*}
            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}H(t^*)^{sk_i}\,|\,i\in U\rangle\,,
        \end{equation*}
        for an unknown $b \in \{0,1\}$. Multiply series elements by $r_i^N,\,1 \leq i \leq n$ for randomly chosen $r_i \in \mathbb{Z}_N$ and return
        \begin{equation*}
            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}r_i^N H(t^*)^{sk_i}\,|\,i\in U\rangle
        \end{equation*}
        to $\mathcal{A}$.
        \item[Guess] When $\mathcal{A}$ makes guess $b'$, make the same guess $b'$ to $\mathcal{C}$.
    \end{description}

@@

\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize,scale=0.9375]
    % Prediction
    \draw [gray] (0,1.75) rectangle (8,8);
    \node at (4,7.5) {1. Prediction};

@@

    % Measurement
    \draw [gray] (0,-4.75) rectangle (8,1.5);
    \node at (4,1) {2. Measurement};

@@

    % Update
    \draw [gray] (0,-10.25) rectangle (8,-5);
    \node at (4,-5.5) {3. Update};

@@

Code was written in the C programming language, using the MPI library \cite{OpenMPI2020} to support simultaneous computations by sensors and navigator via different processes. The OpenSSL library's \cite{OpenSSL2020} mask generation function MGF1 and hash function SHA256 were used to implement the required hash function $H$, while the Libpaillier library \cite{Libpaillier2010} was used for the implementation of the Paillier encryption scheme. Additionally, GNU libraries GSL \cite{GSLGNUScientific2019} and GMP \cite{GMPGNUMultiple2020} were used for algebraic operations and the handling of multiple-precision integers, respectively. Simulation execution was performed on a 3.00GHz Intel i7-9700 CPU, and run on the Windows Subsystem for Linux (WSL), where no real-time kernel was ensured but sufficiently consistent runtimes were observed for the purposes of our simulation.

Figure \ref{fig:sim_timing} shows

@@

 \begin{figure}[htbp]
    \begin{center}
       \includegraphics{images/layouts.pdf}
    \end{center}
    \caption{Layouts Normal Big}
    \label{fig:sim_layouts}
 \end{figure}
